\chapter{Summary}
\label{ch:summary}

This associate thesis describes the development and integration of a digital signature module within the cloud platform Recytix. Previously, an integrated solution for digitally signing documents, such as contracts and mandates, was missing. This resulted in inefficient processes and administrative burdens.

The goal of this project was to realize a working prototype that allows users to sign documents in a legally binding way without leaving the application. The focus was on usability and security.

A modern technology stack was chosen for the realization, aligning with the standards of IRC Engineering. The frontend was developed in \textbf{React} with TypeScript, ensuring a responsive user interface. The backend was realized in \textbf{C\# (.NET)}, with a RESTful API handling communication. A \textbf{PostgreSQL} database is used for data storage and the audit trail.

The core functionality of the module includes viewing PDF documents and signing them via a Two-Factor Authentication (2FA) mechanism using SMS. Every step in the process is accurately recorded in an audit trail, which is essential for legal proof.

The result is a functional and secure module that seamlessly integrates with the existing user authentication of Recytix. This significantly reduces the turnaround time of administrative processes and lays a solid foundation for further expansions, such as integration with Itsme or support for multiple signatories.

\vspace{1.5cm}
\noindent \textbf{Link to GitHub repository (Report):} \\
\url{https://github.com/Lennert08/graduaatsproef-hogent}